Using Interactive Graphics to Visualize Evening Grosbeak Movement and Migration Patterns

### 2024-05-10 paper.qmd
still need basic leaflet section, R Shiny Results code, and conclusion

---
title: Using Interactive Graphics to Visualize Evening Grosbeak Movement and Migration Patterns
author:
  - name: Grace Bridge
---

@@

-   Include code
-   describe data wrangling and data cleaning (dplyr etc.)
-   interpretations of the data - describe leaflet

@@

-   initial cleaning
-   getting to species
-   getting unique bird IDs

@@

-   screenshots of app
-   visualizations
-   leaflet maps of deployments
-   leaflet maps of winter spots
- you can talk obout what is seen a bit, don't have to go into detail about whether or not the data makes sense (just is it summarizing what we intend it to summarize, is it actually doing what I claim its doing. The experts actually analyze it.)

@@

![Interactive Evening Grosbeak Platform](deployments.png){.lightbox}

@@

![Deployments map](output-onlinegiftools.gif){.lightbox}

@@

![Chosen bird map](chosenbird.png){.lightbox}
![Chosen group map](chosengroup.png){.lightbox}

@@

![Winter roosting location map](wintermap.png){.lightbox}
![Winter roosting group map](wintergroups.png){.lightbox}

@@

## Discussion
-  obstacles 
-   future applications
-   bio/data science student to build off of this starter app and analyze what is actually happening
-   needs more data cleaning (birds in south america should not be showing up) (find a map that shows bird in South America and say what you can learn from these shiny app results to further clean the data)
-   summer spots
-   more widgets for timelines (slider input to pick a time period to plot a bird)

@@

### Future and Improvements

>>>>

---
title: Using Interactive Graphics to Visualize Evening Grosbeak Movement and Migration Patterns
author:
  - name: Grace Bridge
lightbox: true
---

@@

@@

@@

@@

![Interactive Evening Grosbeak Platform](deployments.png)

@@

![Deployments map](output-onlinegiftools.gif)

@@

![Chosen bird map](chosenbird.png)
![Chosen group map](chosengroup.png)

@@

![Winter roosting location map](wintermap.png)
![Winter roosting group map](wintergroups.png)

@@

![Data table page](data.png)

## Discussion

@@

### Future and Improvements
<p>A main goal of this project was to create a platform that can be expanded upon. This is a great base for a future student with the knowledge, background, and tools to improve on the features, create more visualizations, and analyze the patterns of the birds. Advanced versions of these visualizations in the hands of the right student researcher will be able to lead them to a conclusion about why the Evening Grosbeak population is declining so rapidly. </p>

<p>Some suggestions for improvement on this app are the following. Upon further research of the Evening Grosbeak habitats, sift through the data and take out faulty data (such as the birds showing up in South America when they should not be). Use the plots provided to discover more data that may not be accurate. Also, add features to see the bird's routes over a specific timeline. This could be done with a sliderInput (over time) to pick a specific time period (possibly from winter roosting to breeding, or summer to summer). </p>

![Bird 75503.45382](southamerica.png)
